Towards a general mathematical theory of experimental science

### 2018-06-14 Articles/TowardsAGeneralMathematicalTheoryOfExperimentalScience/article.tex
Adding acknowledgements

In this paper we briefly present the starting point for our general mathematical theory of experimental science. It is the product of a decade spent in reverse engineering the laws of particle mechanics\cite{Carc1} and our subsequent work on formalizing the starting points.\cite{Carc2} Our overall program is large and ambitious and a journal article cannot treat it comprehensively. Therefore we will only present an overview of the basic concepts, which are already well consolidated and provide a good template to understand our approach. We will only provide a sketch for the proofs, which can be found in our open access book\cite{Carc3} together with more details, discussions and insights.

@@

@@

	\bibitem{Carc2} C. A. Aidala, G. Carcassi, M. J. Greenfield: Topology and experimental distinguishability. arXiv:1708.05492

	\bibitem{Carc3} G. Carcassi, C. A. Aidala: Assumptions of Physics, v0.1. http://assumptionsofphysics.org/book/, Ann Arbor, MI, USA, 2018.
\end{thebibliography}

>>>>

In this paper we briefly present the starting point for our general mathematical theory of experimental science. It is the product of a decade spent in reverse engineering the laws of particle mechanics\cite{Carc1} and our subsequent work on formalizing the starting points.\cite{Carc2} Our overall program is large and ambitious and a journal article cannot treat it comprehensively. Therefore we will only present an overview of the basic concepts, which are already well consolidated and provide a good template to understand our approach. We will only provide a sketch for the proofs, which can be found in the draft of our open access book\cite{Carc3} together with more details, discussions and insights.

@@

\section{Acknowledgments}

We thank Mark J. Greenfield for the thorough review of the mathematical framework. We thank Josh Hunt for comments on the philosophical underpinning of this work. We would also like to acknowledge the numerous individuals who commented on the drafts of this paper and our previous works leading up to it.

@@

	\bibitem{Carc2} C. A. Aidala, G. Carcassi, M. J. Greenfield: Topology and experimental distinguishability. arXiv:1708.05492, 2017.

	\bibitem{Carc3} G. Carcassi, C. A. Aidala: Assumptions of Physics (in preparation). http://assumptionsofphysics.org/book/, Ann Arbor, MI, USA, 2018.
\end{thebibliography}
